---
title: "Participation_Grades"
author: "Lauren Mabe"
date: "6/7/2021"
output: 
  html_document:
    theme: journal
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file will count the number of chats each student's name is found in.  
It will NOT count the number of times they chatted, only if they were there or not  

All files are saved in the same folder, this is specified by mypath variable  
- all chats are .txt files called meeting_saved_chat#.txt  
- Class roster is .csv downloaded directly from Canvas, it has all students and all grades

Run each chunk once, result will be saved as .csv in the attendance folder 

IMPORTANT NOTE: This is not perfect and the chats should be manually reviewed before entering grades  
Known issues:  
- Students with the same last name will be counted twice, will need to be manually fixed after  
- Students whose last names on Canvas and in Zoom dont match will not be counted 
- Students w/ more than 1 last name (Ex: Yeon Chu Paek) will not be counted. Hyphenated last names will be counted  

Basically, anyone w/ 0 attendance should be double checked  

# Load data
## Class Roster  
This is the entire gradebook downloaded from Canvas. It should be moved to the attendance folder and can be renamed  
Section names should exactly match the csv
```{r}


mypath <- "C:/Users/Lauren Mabe/Documents/Z_Old_Classes/TA_AMS_55/attendance/"

# entire canvas gradebook (I renamed it)
roster <- read.csv(paste0(mypath, "all_students_canvas.csv"))

# get only students from my sections
roster <- roster[roster$Section %in% c("AMS 055 A01 SQ 2021", "AMS 055 A02 SQ 2021",
                                        "FST 055 A01 SQ 2021", "FST 055 A02 SQ 2021"), 
                     which(names(roster) %in% c("Student", "Section"))]


# split the student name column w/ strsplit(),
# t() & as.data.frame() turn to df, [,1] grabs last name column
roster$last_name <- t(as.data.frame(strsplit(roster$Student, ","), fix.empty.names = FALSE))[,1]

# this is part of the merge
roster$present <- 0


head(roster)

```

## Zoom Chats
Zoom chats are saved in the attendance folder and are simply named "meeting_saved_chat#" and numbered 1:x  
This chunk separates each line of the txt file, pulling out the "From Student Name" portion of the chat line  
From there, it separates again and grabs the last name.  
If the student put multiple things in the chat, their name is still only counted once  
```{r}

chats <- list()

# loop through folder, make list of text files
for (i in 1:18) {
    
    # read chat txt file
    txtfile <- read.delim(paste0(mypath, "meeting_saved_chat", i, ".txt"), header = FALSE)
    
    # clean the text file up
    # there are better ways to do this, but I wanted to use base R
    # even then, still might be better ways to avoid lists w/in lists, but oh well lol
    
    
    # get only second column (chat column), becomes a vector
    txtfile <- txtfile[,2]
    
    # separate each line where the : is
    # "From Student Name :" the chat message
    # returns each line as list of strings
    txtfile <- sapply(txtfile, strsplit, split = " : ", USE.NAMES = FALSE)
    
    # get the "From Student Name" portion. Its first part of vector
    txtfile <- lapply(1:length(txtfile), function(x) txtfile[[x]][1])
    
    # split that again by the spaces. There are multiple spaces in some places
    # returns a list again
    txtfile <- lapply(txtfile, strsplit, split = " ")
    
    # create a df of last names
    # sapply returns vector
    # it grabs the name in the 5th postition of the vector
    # unique gets each student only once
    txtfile <- data.frame(last_name = unique(sapply(1:length(txtfile), function(x) txtfile[[x]][[1]][5])))

    
    # this column gets attached to the roster df in next chunk
    txtfile$present <- 1
    
    # cleaned text file added to the chats list
    chats[[i]] <- txtfile
    
    
    
} # close for loop


chats[[1]]




```

# Calculate Participation
```{r}

# loop through chats
# merge the chat to the main roster df
# will create new columns named "present.x" or "present.y". Same colnames is fine, ignore warning
for (i in chats) {
    
    roster <- merge(roster, i, by = "last_name", all.x = TRUE,)
    
} # close for loop

# add "present" columns together. 
roster$num_present <- rowSums(roster[,4:ncol(roster)], na.rm = TRUE)



head(roster)


```

# Save participation file
Saves to same place as the rest is saved
```{r}

# does not save the "present" columns
write.csv(roster[,c(1:3, ncol(roster))], paste0(mypath, "Participation_Grades.csv"))

```


